Canadian Family

### 2022-03-18 output/paper 3.Rmd
first

---
title: "Untitled"
author: "Jiayi Du"
date: "2022/3/17"
output: pdf_document
---

```{r}
gss<-read.csv("gss.csv",header=TRUE)
gss<-gss%>%select(age,feelings_life,sex,marital_status,education,hh_size,average_hours_worked,income_family,income_respondent)
```

>>>>

---
title: "Canadian Family"
subtitle: "My subtitle if needed"
author: 
  - Alicia Yang
  - [Another author]
  - []
thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r}
gss<- read_csv(here::here(".Factors-that-affect-happiness/input/gss_family.csv"))
gss<-gss%>%select(age,feelings_life,sex,marital_status,education,hh_size,average_hours_worked,income_family,income_respondent)
```
